---
title: "Major Air Pollutants in NYC and Los Angeles 7-22-2024"
author: "doctahmanhattan"
output: 
  html_document:
    self_contained: yes
---
Introduction
This presentation provides an analysis of major air pollutants in New York City (NYC) and Los Angeles. The pollutants considered in this analysis are PM2.5, PM10, and NO2.

Data Summary
The data used in this presentation is simulated for illustrative purposes.

PM2.5: Fine particulate matter with a diameter of less than 2.5 micrometers.
PM10: Particulate matter with a diameter of less than 10 micrometers.
NO2: Nitrogen dioxide.

```{r setup, include=FALSE}
# Load necessary libraries
library(plotly)
library(dplyr)
```

```{r}
# Set up the data
set.seed(123)
data <- data.frame(
  city = rep(c("NYC", "Los Angeles"), each = 100),
  PM2.5 = c(rnorm(100, mean = 12, sd = 5), rnorm(100, mean = 18, sd = 7)),
  PM10 = c(rnorm(100, mean = 25, sd = 10), rnorm(100, mean = 30, sd = 12)),
  NO2 = c(rnorm(100, mean = 15, sd = 7), rnorm(100, mean = 20, sd = 8))
  )

```

```{r}
# Create a 3D scatter plot with Plotly
plot <- plot_ly(data, x = ~PM2.5, y = ~PM10, z = ~NO2, color = ~city, colors = c('#1f77b4', '#ff7f0e')) %>%
  add_markers() %>%
  layout(scene = list(
    xaxis = list(title = 'PM2.5'),
    yaxis = list(title = 'PM10'),
    zaxis = list(title = 'NO2')
  ))
```
# Save the plot to an HTML object
```{r} 
plot
```